Modelling last glacial cycle ice dynamics in the Alps

### 2017-11-15 articles/cycle/alps-cycle.tex
Make two small fixes. First revision complete.

    For instance the Rhine Glacier (Fig.~\ref{fig:profiles}a) reaches a length
    exceeding 130\,km, roughly corresponding to the location of the last major
    Alpine reliefs and the beginning of the foothills, six times during the
    simulation, and sometimes retreats almost completely between two advances
    (Fig.~\ref{fig:profiles}b). The Rhone Glacier, fed by several high-altitude
    accumulation areas, advanced eight times onto modern Lake Geneva
    (Fig.~\ref{fig:profiles}c and d). The Dora Baltea Glacier, characterised
    by a very steep catchment, and mutliple tributaries, shows even a higher
    variability and reaches close to its maximum position six times throughout
    the simulation (Fig.~\ref{fig:profiles}e and f). The Isère and Inn
    glaciers, with their complex system of confluences and diffluences, need
    longer time to build up and reach the foreland only two and three times
    (Fig.~\ref{fig:profiles}g--j). Finally, the Tagliamento Glacier, distant
    from the major ice-dispersal centres of the inner Alps, is absent for most
    of the modelled glacial cycle (Fig.~\ref{fig:profiles}k and l)

@@

    These results are nevertheless limited by the simplicity of the climate
    forcing and surface mass balance model applied, and uncertainties in ice
    flow physics. For instance, additional climate variability over Central
    Europe may have caused additional glaciations to those modelled here.
    Through more detailed sensitivity studies, targeted to
    specific aspects of the last glacial cycle ice dynamics in the Alps, future
    modelling studies will certainly be able to quantify uncertainties
    associated with some of the above statements. Nevertheless, we hope that
    these conclusions will also serve as a basis for future studies of glacial
    geology in the Alps, and call for a more systematic aggregation and
    homogenization of glacial geological data to form a basis for model
    validation across the entire Alpine range.

>>>>

    For instance the Rhine Glacier (Fig.~\ref{fig:profiles}a) reaches a length
    exceeding 130\,km, roughly corresponding to the location of the last major
    Alpine reliefs and the beginning of the foothills, six times during the
    simulation, and sometimes retreats almost completely between two advances
    (Fig.~\ref{fig:profiles}b). The Rhone Glacier, fed by several high-altitude
    accumulation areas, advanced eight times onto modern Lake Geneva
    (Fig.~\ref{fig:profiles}c and d). The Dora Baltea Glacier, characterised
    by a very steep catchment, and mutliple tributaries, shows even a higher
    variability and reaches close to its maximum position six times throughout
    the simulation (Fig.~\ref{fig:profiles}e and f). The Isère
    (Fig.~\ref{fig:profiles}g and h) and Inn (Fig.~\ref{fig:profiles}i and j)
    glaciers, with their complex system of confluences and diffluences, need
    longer time to build up and reach the foreland only two and three times
    (Fig.~\ref{fig:profiles}g--j). Finally, the Tagliamento Glacier, distant
    from the major ice-dispersal centres of the inner Alps, is absent for most
    of the modelled glacial cycle (Fig.~\ref{fig:profiles}k and l)

@@

    These results are nevertheless limited by the simplicity of the climate
    forcing and surface mass balance model applied, and uncertainties in ice
    flow physics. In particular, additional palaeo-climate variability over
    Central Europe may have caused more glaciations than modelled here.
    Through more detailed sensitivity studies, targeted to
    specific aspects of the last glacial cycle ice dynamics in the Alps, future
    modelling studies will certainly be able to quantify uncertainties
    associated with some of the above statements. Nevertheless, we hope that
    these conclusions will also serve as a basis for future studies of glacial
    geology in the Alps, and call for a more systematic aggregation and
    homogenization of glacial geological data to form a basis for model
    validation across the entire Alpine range.
